Spatial Reasoning and Statistical Graphics

### 2014-11-20 Paper/Draft1/TestingVisualAptitude.Rnw
Move mean-adjusted aptitude test PCA up

>>>>

\paragraph{Removing the effect of overall aptitude}

<<removeAptitude,echo=F,fig.width=8, fig.height=4>>=
vistests <- scale(lineup.section.summary[,c("card_rot", "fig_class", "folding", "vis_search")])
lineups <- scale(lineup.section.summary[,c("lineup_1", "lineup_2", "lineup_3")])
vmain <- rowSums(vistests)/4
alltests <- data.frame(vmain, vistests-vmain, lineups)
pctests <- prcomp(alltests)
par(mfrow=c(1,2), mar=c(4,4.5,.1,.1), tcl=-0.01, cex.lab=.8,cex.axis=.7,mgp=c(2,.7,0),tcl=-.3)
biplot(pctests)
biplot(pctests, 3:4)
@
